### 2020-09-11 prf/lem-pgv-value-done.tex
Fixed case environment.

\begin{proof}
  By induction on the derivation of $\tseq[\cs{o}]{\ty{\Gamma}}{V}{T}$.
  \begin{case}[\LabTirName{T-Lam}]
    Immediately.
    \begin{mathpar}
      \inferrule*{
        \tseq[\cs{o}]{\ty{\Gamma},\tmty{x}{T}}{M}{U}
      }{\tseq[\cs{\pbot}]{\ty{\Gamma}}{\lambda x.M}{\tylolli[\cs{\pr(\ty{\Gamma})},\cs{o}]{T}{U}}}
    \end{mathpar}
  \end{case}
  \begin{case}[\LabTirName{T-Unit}]
    Immediately.
    \begin{mathpar}
      \inferrule*{
      }{\tseq[\cs{\pbot}]{\emptyenv}{\unit}{\tyunit}}
    \end{mathpar}
  \end{case}
  \begin{case}[\LabTirName{T-Pair}]
    The induction hypotheses give us $\cs{p}=\cs{q}=\cs{\pbot}$, hence $\cs{p}\sqcup\cs{q}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr(\ty{T})$ and $\pr(\ty{\Delta})=\pr(\ty{U})$, hence $\pr(\ty{\Gamma},\ty{\Delta})=\pr(\ty{\Gamma})\sqcap\pr(\ty{\Delta})=\pr(\ty{T})\sqcap\pr(\ty{U})=\pr(\ty{\typrod{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[\cs{p}]{\ty{\Gamma}}{V}{T}
        \\
        \tseq[\cs{q}]{\ty{\Delta}}{W}{U}
        \\
        \cs{p}<\pr(\ty{\Delta})
      }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\pair{V}{W}}{\typrod{T}{U}}}
    \end{mathpar}
  \end{case}
  \begin{case}[\LabTirName{T-Inl}]
    The induction hypothesis gives us $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr{\ty{T}}$. We know $\pr(\ty{T})=\pr({\ty{U}})$, hence $\pr(\ty{\Gamma})=\pr(\ty{\tysum{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[o]{\ty{\Gamma}}{V}{T}
        \\
        \pr(\ty{T})=\pr(\ty{U})
      }{\tseq[o]{\ty{\Gamma}}{\inl{V}}{\tysum{T}{U}}}
    \end{mathpar}
  \end{case}
  \begin{case}[\LabTirName{T-Inr}]
    The induction hypothesis gives us $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr{\ty{U}}$. We know $\pr(\ty{T})=\pr({\ty{U}})$, hence $\pr(\ty{\Gamma})=\pr(\ty{\tysum{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[o]{\ty{\Gamma}}{V}{U}
        \\
        \pr(\ty{T})=\pr(\ty{U})
      }{\tseq[o]{\ty{\Gamma}}{\inr{V}}{\tysum{T}{U}}}
    \end{mathpar}
  \end{case}
\end{proof}

>>>>

\begin{proof}
  By induction on the derivation of $\tseq[\cs{o}]{\ty{\Gamma}}{V}{T}$.
  \begin{case*}[\LabTirName{T-Lam}]
    Immediately.
    \begin{mathpar}
      \inferrule*{
        \tseq[\cs{o}]{\ty{\Gamma},\tmty{x}{T}}{M}{U}
      }{\tseq[\cs{\pbot}]{\ty{\Gamma}}{\lambda x.M}{\tylolli[\cs{\pr(\ty{\Gamma})},\cs{o}]{T}{U}}}
    \end{mathpar}
  \end{case*}
  \begin{case*}[\LabTirName{T-Unit}]
    Immediately.
    \begin{mathpar}
      \inferrule*{
      }{\tseq[\cs{\pbot}]{\emptyenv}{\unit}{\tyunit}}
    \end{mathpar}
  \end{case*}
  \begin{case*}[\LabTirName{T-Pair}]
    The induction hypotheses give us $\cs{p}=\cs{q}=\cs{\pbot}$, hence $\cs{p}\sqcup\cs{q}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr(\ty{T})$ and $\pr(\ty{\Delta})=\pr(\ty{U})$, hence $\pr(\ty{\Gamma},\ty{\Delta})=\pr(\ty{\Gamma})\sqcap\pr(\ty{\Delta})=\pr(\ty{T})\sqcap\pr(\ty{U})=\pr(\ty{\typrod{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[\cs{p}]{\ty{\Gamma}}{V}{T}
        \\
        \tseq[\cs{q}]{\ty{\Delta}}{W}{U}
        \\
        \cs{p}<\pr(\ty{\Delta})
      }{\tseq[\cs{p}\sqcup\cs{q}]{\ty{\Gamma},\ty{\Delta}}{\pair{V}{W}}{\typrod{T}{U}}}
    \end{mathpar}
  \end{case*}
  \begin{case*}[\LabTirName{T-Inl}]
    The induction hypothesis gives us $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr{\ty{T}}$. We know $\pr(\ty{T})=\pr({\ty{U}})$, hence $\pr(\ty{\Gamma})=\pr(\ty{\tysum{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[o]{\ty{\Gamma}}{V}{T}
        \\
        \pr(\ty{T})=\pr(\ty{U})
      }{\tseq[o]{\ty{\Gamma}}{\inl{V}}{\tysum{T}{U}}}
    \end{mathpar}
  \end{case*}
  \begin{case*}[\LabTirName{T-Inr}]
    The induction hypothesis gives us $\cs{o}=\cs{\pbot}$, and $\pr(\ty{\Gamma})=\pr{\ty{U}}$. We know $\pr(\ty{T})=\pr({\ty{U}})$, hence $\pr(\ty{\Gamma})=\pr(\ty{\tysum{T}{U}})$.
    \begin{mathpar}
      \inferrule*{
        \tseq[o]{\ty{\Gamma}}{V}{U}
        \\
        \pr(\ty{T})=\pr(\ty{U})
      }{\tseq[o]{\ty{\Gamma}}{\inr{V}}{\tysum{T}{U}}}
    \end{mathpar}
  \end{case*}
\end{proof}
